---
title: "p8105_hw1_kw2873"
author: "Keyi Wang"
date: "9/13/2019"
output: github_document
---

I'm an R Markdown document! 

# problem 1: datafram

```{r include=FALSE }
library(tidyverse)
```

```{r}

  set.seed(12) 
  s = rnorm(8)
  v_logi = s > 0
  v_ch = c("yellow", "blue", "green", "red","black", "white", "gray", "purple")
  v_fac = factor(c("AB", "B", "O", "B","B", "O", "AB", "B"),
                 levels = c('AB','B','O'))
  example_df = tibble(
  samp = s,
  vec_logical = v_logi,
  vec_char = v_ch,
  vec_factor = v_fac
  )
### using the as.numeric function
numeric_logi = as.numeric(v_logi)
numeric_ch = as.numeric(v_ch)
numeric_fac = as.numeric(v_fac)
```
Both logic vector and factor vector can be transformed into numeric vector but factor vector failed to do so. 
For logic vecor, R recognize True as 1 , False as 0. Therefore, when we use the as.numeric function, R can easily 
take True as 1 and False as 0. Smilarly,factor vector has level which can be recognized by R as 1,2,3 and so on. 
Therefore, as.numeric fucntion can be applied here sucessfully. However, R can not recognize character vector as numeric factor.

When it comes to taking the  mean of these vectors: the mean of my sample is `r mean(s)`. the mean of my logical vector is `r mean(v_logi)`, the mean of my character vector is `r mean(v_ch)` and the mean of my character vector is `r mean(v_ch)`.
As mentioned before, since R take True and False as 1 and 0, we can take the mean of logical vector. 
Since R can not recognize factor and charactor as numeric vectors, we can not take mean from it. 

# **problem 1 continued**
```{r}
### vector convertion using as.numeric function
new_logi1 = as.numeric(v_logi)
new_logi2 = as.factor(v_logi)
result1 = new_logi1*s
result2 = new_logi2*s
new_logi3 = as.numeric(new_logi2)
result3 = new_logi3*s
```

# problem 2
```{r}
### creating dataframe for making boxplot
set.seed(1)
x = rnorm(500)
library(tidyverse)
plot_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  v_logi = x + y > 1,
  v_num = as.numeric(v_logi),
  v_fac = as.factor(v_num),
)
new_logi = pull(plot_df,v_logi) ### pulling out the data from dataframe in order to 
                                ### calculate for the proportion                                          
```
In this dataplot, the number of rows is `r nrow(plot_df)`
the number of colon is `r ncol(plot_df)` 
the mean, meadian, and standard deviation of x are
`r mean(x)`, `r median(x)`, `r var(x)` respectively.
And the proportion for cases for which x+y>1 is  `r sum(new_logi)`/ `r length(x)`

# problem 2 continued with making plots
```{r}
ggplot(plot_df, aes(x = x, y = y, color = v_logi)) + geom_point() 
ggsave("scatterplot1.png")
ggplot(plot_df, aes(x = x, y = y, color = v_num)) + geom_point()
ggplot(plot_df, aes(x = x, y = y, color = v_fac)) + geom_point()
 





