---
title: "p8105_hw1_kw2873"
author: "Keyi Wang"
date: "9/13/2019"
output: github_document
---

I'm an R Markdown document! 

# problem 1: datafram


```{r}
  set.seed(12)
  s = rnorm(8)
  v_logi = s > 0
  v_ch = c("A", "B", "C", "D","E", "F", "G", "H")
  v_fac = factor(c("AB", "B", "O", "B","B", "O", "AB", "B"),
                 levels = c('AB','B','O'))
  
library(tidyverse)
example_df = tibble(
  samp = s,
  vec_logical = v_logi,
  vec_char = v_ch,
  vec_factor = v_fac
  )
### out put of the example_data fram
example_df
### take the mean of each variables
mean(s)
mean(v_logi)
mean(v_ch)
mean(v_fac)
### using the as.numeric function

as.numeric(v_logi)
as.numeric(v_ch)
as.numeric(v_fac)
```
the mean of my sample is `r mean(s)`

the mean of my logical vector is `r mean(v_logi)`

the mean of my character vector is `r mean(v_ch)`

the mean of my factor vector is `r mean(v_fac)`

**we noticed that the mean of both character  and factor vector
doesn't exist. However, when I used the as.numeric function to 
convert the non-numeric ve **


# problem 1 continued 
```{r}
new_logi1 = as.numeric(v_logi)
new_logi2 = as.factor(v_logi)
result1 = new_logi1*s
result2 = new_logi2*s
new_logi3 = as.numeric(new_logi2)
result3 = new_logi3*s
```

# problem 2
```{r}
set.seed(1)
x = rnorm(500)
library(tidyverse)
plot_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  v_logi = x + y > 1,
  v_num = as.numeric(v_logi),
  v_fac = as.factor(v_num),
)
summary(plot_df)
```
In this dataplot, the number of rows is `r nrow(plot_df)`
the number of colon is `r ncol(plot_df)` 
the mean, meadian, and standard deviation of x are
`r mean(x)`, `r median(x)`, `r var(x)` respectively.
And the proportion for cases for which x+y>1 is 25.2% 

# problem 2 continued with making plots
```{r}
plot_1 = ggplot(plot_df, aes(x = x, y = y, color = v_logi)) + geom_point()
plot_2 = ggplot(plot_df, aes(x = x, y = y, color = v_num)) + geom_point()
plot_3 = ggplot(plot_df, aes(x = x, y = y, color = v_fac)) + geom_point()
ggsave("scatterplot1.png", plot=plot_1)
```




